Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Atmosphere from Space \tnoteref{tnote1}

### 2022-12-03 paper/sTEC-time_series.tex
Synchronize MDPI paper with overleaf

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{../figures/caribbean-Dst-index.pdf}
    \caption{Dst index for 2019 June 22th. Data obtained from WDC for Geomagnetism, Kyoto DST index service.}
    \label{fig:Dst_index}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{../figures/solar_speed_all_wcs.pdf}
    \caption{Relative speed of solar wind at the event day and previous week respect the previous day, normalized with speed of sound. Each curve represents one day data.}
    \label{fig:solar-relative-speed}
\end{figure*}

@@

Finally we wanted to check the effects of solar cycle variations. The critical frequencies of reflection $f_c$ is proportional to the number of sunspots in the Sun, thus affecting our TEC measurements. Seasonal variations may be important too, since solar flux varies as the Earth revolves around the Sun. To measure these effects, we computed dTEC, defined as:

@@

\begin{table}
    \centering
    \caption{W index values with their corresponding dTEC values and a brief description of the ionospheric state when thos index is obtained.}
    \begin{tabular}{lcr}\toprule
    dTEC & W index   & Ionospheric state     \\
    \hline
    $dTEC = 0$ & 0   & Reference quiet state \\
    $0<|dTEC|<0.046$ & $\pm 1$ & Quiet state \\
    $0.046<|dTEC|<0.155$ & $\pm 2$ & Weak perturbation \\
    $0.155<|dTEC|<0.301$ & $\pm 3$ & Moderated storm   \\
    $|dTEC|> 0.301$  & $\pm 4$ & Intense storm         \\\bottomrule
    \end{tabular}
    \label{tab:W-index}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../figures/dTEC_Windex_boav.pdf}
    \caption{dTEC and W index for station BOAV. dTEC is shown as the continuous blue curve. The corresponding W index ranges are shown as the colored backgrounds, from quiet state in blue to strong storm $(|W|=4)$ in red. The meteor fragmentation time is shown in vertical dashed line, and  as additional information the local sunrise and sunset in dashed blue lines.}
    \label{fig:dtec-boav}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../figures/BOAV-KOUG-KOUR-sunset.pdf}
    \caption{Solar terminator position for the most southern stations: BOAV (yellow shadow), KOUG and KOUR (gray shadow). The corresponding sunset times are labeled in the corresponding terminator line, and the sunset time difference between KOUG and KOUR stations is just 2 minutes. Sunset time in stations KOUR and KOUG occured 20 minutes later than meteor fragmentation.}
    \label{fig:solar_terminator}
\end{figure}

\begin{figure*}
    \centering
    \begin{tabular}{ccc}
    \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN2.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN2.pdf}& \includegraphics[width=0.3\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf} \\
\includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN12.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN12.pdf} & \includegraphics[width=0.3 \linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}
    \end{tabular}
    \caption{Detrended sTEC time series for station KOUG for the days 2019-06-19, 2019-06-20 and 2019-06-22 (three days before meteor fall, two days and the meteor fall date, from left to right). The satellite receiver LOS with PRN 2 is in top, and the LOS with PRN 12 is in bottom.}
    \label{fig:solar_terminator_time_series}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2.pdf}\\
%    \includegraphics[width=0.3\linewidth]{}  \includegraphics[width=0.3\linewidth]{}\\
    \end{tabular}
    \caption{sTEC time series for stations where TIDs are likely to be detected. In the left panels we show the time series for the previous day of meteor fall, and in the right panels the time series for the meteor fall date.}
    \label{fig:sTEC-series}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12.pdf}\\
    \end{tabular}
    \caption{Continuation of figure \ref{fig:sTEC-series}}
    \label{fig:sTEC-series2}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2.pdf}
    \end{tabular}
    \caption{Continuation of figures \ref{fig:sTEC-series} and \ref{fig:sTEC-series2}.}
    \label{fig:sTEC-series3}
\end{figure*}

@@

\begin{figure*}
    \begin{tabular}{cc}
      \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-boav-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn04-polar-hlght.pdf} \\
            \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn40-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-gre1-polar-hlght.pdf} \\
     \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-koug-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-ttsf-polar-hlght.pdf} \\
    \end{tabular}
    \label{fig:azimuth-elevations-maps-1}
    \caption{Azimuth-Elevation maps for GPS stations which presumably detected TIDs. In colored curves we show the satellites trajectories with their respective label. The black dots are the meteor trajectory using the GLM data and the magenta dashed curve represent the meteor trajectory using the velocity parameters from table \ref{tab:Meteor-parameters}.}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/boav_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/cn04_satellites_positions_terminator_21-25-48.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/cn40_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1_satellites_positions_terminator_21-25-48.pdf} \\
    \includegraphics[width=0.45\linewidth]{../figures/koug_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/ttsf_satellites_positions_terminator_21-25-48.pdf}
    \end{tabular}
    \caption{Position of IPP in the satellite-receiver LoS for the same GPS stations as figure \ref{fig:azimuth-elevations-maps-1}. The GLM data are shown in magenta dots, the fragmentation position in a red star and the estimated trajectory from 1 hour before fragmentation to a few seconds after fragmentation is shown in green dashed line. The position of the GPS station is shown with a blue triangle. The solar terminator appears in BOAV and KOUG stations as a blue shadow.}
    \label{fig:satellites-and-terminator}
\end{figure*}

% The mathematical proccedure to change the GLM data and the estimated trajectory, using the parameters from table \ref{tab:Meteor-parameters}. 
%\subsection{Wavelet power spectrum}

>>>>

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \includegraphics[width=\linewidth]{../figures/caribbean-Dst-index.pdf}
    \end{adjustwidth}
    \caption{Dst index for 2019 June 22th. Data obtained from WDC for Geomagnetism, Kyoto DST index service.}
    \label{fig:Dst_index}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \includegraphics[width=\linewidth]{../figures/solar_speed_all_wcs.pdf}
    \end{adjustwidth}
    \caption{Relative speed of solar wind at the event day and previous week respect the previous day, normalized with speed of sound. Each curve represents one day data.}
    \label{fig:solar-relative-speed}
\end{figure*}

@@

Finally we wanted to check the effects of solar cycle variations. The critical frequencies of reflection $f_c$ is proportional to the number of sunspots in the Sun, thus affecting our TEC measurements. Seasonal variations may be important too, since solar flux varies as the Earth revolves around the Sun. To measure these effects, we computed dTEC, defined as \citep{Gulyaeva:2008}:

@@

\begin{table}
    \centering
    \caption{W index values with their corresponding dTEC values and a brief description of the ionospheric state when those index is obtained \citep{Gulyaeva:2008}.}
    \begin{tabular}{lcr}\toprule
    dTEC & W index   & Ionospheric state     \\
    \hline
    $dTEC = 0$ & 0   & Reference quiet state \\
    $0<|dTEC|<0.046$ & $\pm 1$ & Quiet state \\
    $0.046<|dTEC|<0.155$ & $\pm 2$ & Weak perturbation \\
    $0.155<|dTEC|<0.301$ & $\pm 3$ & Moderated storm   \\
    $|dTEC|> 0.301$  & $\pm 4$ & Intense storm         \\\bottomrule
    \end{tabular}
    \label{tab:W-index}
\end{table}

@@

\begin{figure}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \includegraphics[width=\linewidth]{../figures/dTEC_Windex_boav.pdf}
    \end{adjustwidth}
    \caption{dTEC and W index for station BOAV. dTEC is shown as the continuous blue curve. The corresponding W index ranges are shown as the colored backgrounds, from quiet state in blue to strong storm $(|W|=4)$ in red. The meteor fragmentation time is shown in vertical dashed line, and  as additional information the local sunrise and sunset in dashed blue lines.}
    \label{fig:dtec-boav}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \includegraphics[width=\linewidth]{../figures/BOAV-KOUG-KOUR-sunset.png}
    \end{adjustwidth}
    \caption{Solar terminator position for the most southern stations: BOAV (yellow shadow), KOUG and KOUR (gray shadow). The corresponding sunset times are labeled in the corresponding terminator line, and the sunset time difference between KOUG and KOUR stations is just 2 minutes. Sunset time in stations KOUR and KOUG occured 20 minutes later than meteor fragmentation.}
    \label{fig:solar_terminator}
\end{figure}

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \begin{tabular}{ccc}
    \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-19_PRN2.pdf} & \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-20_PRN2.pdf}& \includegraphics[width=0.33\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf} \\
    \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-19_PRN12.pdf} & \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-20_PRN12.pdf} & \includegraphics[width=0.33\linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}
    \end{tabular}
    \end{adjustwidth}
    \caption{Detrended sTEC time series for station KOUG for the days 2019-06-19, 2019-06-20 and 2019-06-22 (three days before meteor fall, two days and the meteor fall date, from left to right). The satellite receiver LOS with PRN 2 is in top, and the LOS with PRN 12 is in bottom.}
    \label{fig:solar_terminator_time_series}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2.pdf}\\
%    \includegraphics[width=0.3\linewidth]{}  \includegraphics[width=0.3\linewidth]{}\\
    \end{tabular}
    \end{adjustwidth}
    \caption{sTEC time series for stations where TIDs are likely to be detected. In the left panels we show the time series for the previous day of meteor fall, and in the right panels the time series for the meteor fall date.}
    \label{fig:sTEC-series}
\end{figure*}

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12.pdf}\\
    \end{tabular}
    \end{adjustwidth}
    \caption{Continuation of figure \ref{fig:sTEC-series}}
    \label{fig:sTEC-series2}
\end{figure*}

\begin{figure*}
    \centering
    \begin{adjustwidth}{-\extralength}{0cm}
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2.pdf}
    \end{tabular}
    \end{adjustwidth}
    \caption{Continuation of figures \ref{fig:sTEC-series} and \ref{fig:sTEC-series2}.}
    \label{fig:sTEC-series3}
\end{figure*}

@@

\begin{figure*}
\begin{adjustwidth}{-\extralength}{0cm}
    \begin{tabular}{cc}
      \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-boav-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn04-polar-hlght.png} \\
            \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn40-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-gre1-polar-hlght.png} \\
     \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-koug-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-ttsf-polar-hlght.png} \\
    \end{tabular}
    \end{adjustwidth}
    \caption{Azimuth-Elevation maps for GPS stations which presumably detected TIDs. In colored curves we show the satellites trajectories with their respective label, the trajectory starts at the big colored dot. The black dots are the meteor trajectory using the GLM data and the magenta dashed curve represent the meteor trajectory using the velocity parameters from table \ref{tab:Meteor-parameters}.}
    \label{fig:azimuth-elevations-maps-1}
\end{figure*}

\begin{figure*}
\begin{adjustwidth}{-\extralength}{0cm}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.5\linewidth]{../figures/boav_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{../figures/cn04_satellites_positions_terminator_21-25-48.png}\\
    \includegraphics[width=0.5\linewidth]{../figures/cn40_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{../figures/gre1_satellites_positions_terminator_21-25-48.png} %\\
   % \includegraphics[width=0.5\linewidth]{figures/koug_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{figures/ttsf_satellites_positions_terminator_21-25-48.png}
    \end{tabular}
    \end{adjustwidth}
    \caption{Position of IPP in the satellite-receiver LoS for the same GPS stations as figure \ref{fig:azimuth-elevations-maps-1}. The GLM data are shown in magenta dots, the fragmentation position in a red star and the estimated trajectory from 1 hour before fragmentation to a few seconds after fragmentation is shown in green dashed line. The position of the GPS station is shown with a blue triangle. The solar terminator appears in BOAV and KOUG stations as a blue shadow.}
    \label{fig:satellites-and-terminator}
\end{figure*}
%The mathematical proccedure to change the GLM data and the estimated trajectory, using the parameters from table \ref{tab:Meteor-parameters}. 
%\subsection{Wavelet power spectrum}
